### 2019-09-05 manuscript/manuscript.tex
updated ms

% line numbers:
\RequirePackage{lineno}
%\modulolinenumbers[5]
\definecolor{linenogray}{gray}{0.75}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{linenogray}}

@@

@@

@@

  \caption{We chose the binsize used in the histograms of Figure
  \ref{fig:figure-3} via an analytic expression for the cross-validation risk,
based on the equation 6.16 of (\cite{Wasserman2006-jl}, p. )}

  \label{suppfig:barghi-cross-validation-binsize}
\end{figure}

>>>>

% line numbers:
\RequirePackage{lineno}
%\modulolinenumbers[5]
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{black}}

@@

\linenumbers
\begin{abstract}

\end{abstract}

@@

A long-standing problem in evolutionary genetics is quantifying the roles drift
and selection have in shaping genome-wide allele frequency changes. Previous
work on this question has focused on teasing apart the impacts of drift and
selection on genome-wide diversity using population samples from a single
contemporary timepoint, usually by modeling the correlation between regional
recombination rate and diversity created in the presence of linked selection
(XXX). While this approach has dramatically informed our present view of the
role of linked selection in shaping genome-wide diversity across a variety of
organisms (XXX), and has allowed us to quantity the relative roles positive
selection (hitchhiking) and negative selection (background selection) have
shaping patterns of genome-wide diversity (XXX), we fully lack an understanding
of how linked selection acts over an important dimension: time.

Presently, there are numerous examples of phenotypes rapidly evolving (XXX),
yet the polygenic nature of fitness makes detecting the impact selection has on
genome-wide variation over short timescales remarkably difficult. This is
because the effect of selection on a polygenic trait (such as fitness) is
distributed across loci proportional to their effect sizes, leading to subtle
allele frequency shifts that are difficult to distinguish from background
levels of genetic drift and sampling variance. However, increasingly genomic
studies with multiple timepoints and, in some cases, multiple replicate
populations are becoming available, used to detect selected loci (XXX) and
differentiate models of selection (XXX). In a previous paper, we proposed that
one signal of polygenic linked selection that could be detected from these
temporal genomic studies is the temporal autocovariance in allele frequency
changes \parencite{Buffalo2019-io}. These covariances are directly estimable
from temporal genomic data and are created only in the presence of linked
selection, but not genetic drift in a closed population.

Here, we provide the first empirical analyses quantify the impact of linked
selection acting over short timescales (tens of generations) across two evolve
and re-sequence studies \parencite{Barghi2019-qy,Kelly2019-dc}, and one
artificial selection experiment \parencite{Castro2019-uk}. We repeatedly find a
signal of temporal covariance, consistent with linked selection acting to
significantly perturb genome-wide allele frequency changes across the genome in
a manner that other approaches would not be able differentiate from genetic
drift. We estimate the lower bound of the proportion of total variation in
allele frequency change caused by linked selection, and the correlation between
allele frequency changes between replicate populations caused by response to
convergent selection pressures. Overall, we demonstrate that linked selection
has a powerful role in shaping genome-wide allele frequency changes over very
short timescales.

@@

  \caption{We chose number of bins used in the histograms of Figure
    \ref{fig:figure-3} via an analytic expression for the cross-validation
    risk, based on the equation 6.16 of (\cite{Wasserman2006-jl}, p. 129).
    Above, we plot the cross-validation risk for various numbers of bins, for
    each of the four off-diagonals of the temporal covariance matrix that we
    analyze. Overall, because the number of data points is large, oversmoothing
    is less of a problem, leading the cross-validation risk to be relatively
    flat across a large number of bins. Each gray point indicates the minimal
    risk for a particular off-diagonal, and the dashed line indicates the best
    average binwidth across off-diagonals.}
  \label{suppfig:barghi-cross-validation-binsize}
\end{figure}
